\textbf{COMP0086 Summative Assignment}

### 2022-11-08 main.tex
fix bug with using same seed for random initialisation

        However, the data generating process for the training data set labels \textit{and} the testing data set labels were injected with noise, so k-values greater than 3 have a ``de-noising'' effect allowing for better performance at around $k=9$.
        As the k-value increases beyond $k=9$, this smoothing effect is too strong, causing the gradual increase in test error as the k value increases.
        For $k<9$ and in particular $k<v=3$ we see the error growing because the model has small $k$ and is able to fit to the noise injected into the data generating process, corrupting the model.

>>>>

        However, the data generating process for the training data set labels \textit{and} the testing data set labels were injected with noise, so k-values greater than 3 have a ``de-noising'' effect allowing for better performance at around $k=7$.
        As the k-value increases beyond $k=7$, this smoothing effect is too strong, causing the gradual increase in test error as the k value increases.
        For $k<7$ and in particular $k<v=3$ we see the error growing because the model has small $k$ and is able to fit to the noise injected into the data generating process, corrupting the model.
